County Results

### 2023-06-24 reports/county_correlations.Rmd
update output files

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=FALSE,warning=FALSE,cache=TRUE)

@@

## Normalization Strategy 1: By Values at Biweek Where Wastewater Concentration is Maximized

@@

## Normalization Strategy 2: By Maximum (Separately)

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=FALSE, warning=FALSE,cache=TRUE, fig.width=10, fig.height=7)

@@

## Normalization Strategy 1: Standardization

w_data <- wjoined %>% 
  select(-date) %>%
  distinct() %>%
  filter(fips %in% counties_with_waste) %>%
  filter(!is.na(mean_conc)) %>%
  group_by(fips, version) %>%
  mutate(mean_conc_std = (mean_conc - mean(mean_conc))/ 
           sd(mean_conc),
         exp_cases_median_std = (exp_cases_median -
                                   mean(exp_cases_median)/sd(exp_cases_median)),
         infections_std = (infections - mean(infections))/sd(infections),
         exp_cases_lb_std = (exp_cases_lb - mean(exp_cases_lb)/ sd(exp_cases_lb)),
        exp_cases_ub_std = (exp_cases_ub - mean(exp_cases_ub)/ sd(exp_cases_ub)),
         positive_std = (positive - mean(positive))/sd(positive))  %>%
  ungroup()

## Normalization Strategy 2: By Values at Biweek Where Wastewater Concentration is Maximized

@@

## Normalization Strategy 3: By Maximum (Separately)
